\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/figures.tex
Future work multiple trigger stages and Model figure updates
Re-ran Bandwidth test and re-generated graph

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model}
    \caption{ General model of speculative computation within the Measure 
        process when triggered. \textit{Speculative Computation} has access
        to all variables which do not require a memory transaction within
        the current state of the process. The process can subsequently make
        \textit{Resultant Computations} based on the value returned from 
        Prime and Probe to update the state of the process. }
    \label{fig:general_model}
\end{figure}
}

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
    \caption{Speculative Bandwidth - Using the speculative primitive 
        1KB of data can be decrypted and exfiltrated at a speed around 5500 kbps
        from the speculative world. Varying the width of the channel 
        results in competing performance factors -- decreasing the 
        number of loops vs decreased size of the probe space.}
    \label{fig:spec_bandwidth}
\end{figure}
}

\newcommand{\FigSpasmModel}{
\begin{figure}[b]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/spasm_model}
    \caption{This model describes the VM control flow. An encrypted SPASM binary 
        stored in dead code or data accessible to \textit{Speculative Computation} 
        is decrypted  and then returned through the primitive. The SPASM 
        \textit{Resultant Computation} performs the SPASM emulation to update the 
        process state before the next instruction is decrypted.}
    \label{fig:spasm_model}
\end{figure}
}

>>>>

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
    \caption{ General model of speculative computation within the Measure 
        process when triggered. \textit{Speculative Computation} has access
        to all variables which do not require a memory transaction within
        the current state of the process. The process can subsequently make
        \textit{Resultant Computations} based on the value returned from 
        \texttt{Flush+Reload} to update the state of the process. }
    \label{fig:general_model}
\end{figure}
}

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
    \caption{Speculative Bandwidth - Using the speculative primitive 
        1KB of data can be decrypted and exfiltrated at a speed between 5 and 6 kbps
        from the speculative world. Varying the width of the channel 
        results in competing performance factors -- decreasing the 
        number of loops vs decreased size of the probe space.}
    \label{fig:spec_bandwidth}
\end{figure}
}

\newcommand{\FigSpasmModel}{
\begin{figure}[b]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/spasm_model.pdf}
    \caption{This model describes the VM control flow. An encrypted SPASM binary 
        stored in dead code or data accessible to \textit{Speculative Computation} 
        is decrypted  and then returned through the primitive. The SPASM 
        \textit{Resultant Computation} performs the SPASM emulation to update the 
        process state before the next instruction is decrypted.}
    \label{fig:spasm_model}
\end{figure}
}
